The title

### 2023-03-21 doc/manuscript.Rmd
Spelling errors fixed

```{r PA-by-sleep-duration-fig, fig.cap = "Physical activty by sleep duration"}
knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activty by sleep efficiency"}
knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig, fig.cap = "Physical activty by sleep onset"}
knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activty by sleep regularity"}
knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age.jpg"), error = FALSE)
```

>>>>

```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration"}
knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency"}
knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset"}
knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity"}
knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age.jpg"), error = FALSE)
```

### 2023-03-21 doc/multiverse.Rmd
Spelling errors fixed

```{r PA-by-sleep-duration-fig, fig.cap = "Physical activty by sleep duration"}
knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age_fixedef.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activty by sleep efficiency"}
knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age_fixedef.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig, fig.cap = "Physical activty by sleep onset"}
knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age_fixedef.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activty by sleep regularity"}
knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age_fixedef.jpg"), error = FALSE)
```

@@

```{r include = FALSE, eval = FALSE}
pattern <- readLines(fs::path("doc/results_chunk.md")) |> paste(collapse = "\n")

@@

@@

```{r PA-by-sleep-duration-fig-by-bmi, fig.cap = "Physical activty by sleep duration moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Bmi.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-bmi, fig.cap = "Physical activty by sleep efficiency moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Bmi.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-bmi, fig.cap = "Physical activty by sleep onset moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Bmi.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-bmi, fig.cap = "Physical activty by sleep regularity moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Bmi.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-ses, fig.cap = "Physical activty by sleep duration moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Ses.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-ses, fig.cap = "Physical activty by sleep efficiency moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Ses.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-ses, fig.cap = "Physical activty by sleep onset moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Ses.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-ses, fig.cap = "Physical activty by sleep regularity moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Ses.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-sex, fig.cap = "Physical activty by sleep duration moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Sex.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-sex, fig.cap = "Physical activty by sleep efficiency moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Sex.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-sex, fig.cap = "Physical activty by sleep onset moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Sex.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-sex, fig.cap = "Physical activty by sleep regularity moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Sex.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-weekday, fig.cap = "Physical activty by sleep duration moderated by weekday"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Weekday_x.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-weekday, fig.cap = "Physical activty by sleep efficiency moderated by weekday"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Weekday_x.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-weekday, fig.cap = "Physical activty by sleep onset moderated by weekday"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Weekday_x.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-weekday, fig.cap = "Physical activty by sleep regularity moderated by weekday"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Weekday_x.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-season, fig.cap = "Physical activty by sleep duration moderated by season"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Season.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-season, fig.cap = "Physical activty by sleep efficiency moderated by season"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Season.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-season, fig.cap = "Physical activty by sleep onset moderated by season"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Season.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-season, fig.cap = "Physical activty by sleep regularity moderated by season"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Season.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-region, fig.cap = "Physical activty by sleep duration moderated by region"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Region.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-region, fig.cap = "Physical activty by sleep efficiency moderated by region"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Region.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-region, fig.cap = "Physical activty by sleep onset moderated by region"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Region.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-region, fig.cap = "Physical activty by sleep regularity moderated by region"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Region.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-daylight, fig.cap = "Physical activty by sleep duration moderated by daylight hours"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Daylight_hours.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-daylight, fig.cap = "Physical activty by sleep efficiency moderated by daylight hours"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Daylight_hours.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-daylight, fig.cap = "Physical activty by sleep onset moderated by daylight hours"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Daylight_hours.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-daylight, fig.cap = "Physical activty by sleep regularity moderated by daylight hours"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Daylight_hours.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-wear-location, fig.cap = "Physical activty by sleep duration moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-wear-location, fig.cap = "Physical activty by sleep efficiency moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-wear-location, fig.cap = "Physical activty by sleep onset moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activty by sleep regularity moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

>>>>

```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration"}
knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age_fixedef.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency"}
knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age_fixedef.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset"}
knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age_fixedef.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity"}
knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age_fixedef.jpg"), error = FALSE)
```

@@

```{r eval = FALSE}
pattern <- readLines(fs::path("doc/results_chunk.md")) |> paste(collapse = "\n")

@@

<!------------------------------------>
<!-- Auto-generated chunks go here: -->
<!------------------------------------>

@@

```{r PA-by-sleep-duration-fig-by-bmi, fig.cap = "Physical activity by sleep duration moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Bmi.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-bmi, fig.cap = "Physical activity by sleep efficiency moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Bmi.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-bmi, fig.cap = "Physical activity by sleep onset moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Bmi.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-bmi, fig.cap = "Physical activity by sleep regularity moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Bmi.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-ses, fig.cap = "Physical activity by sleep duration moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Ses.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-ses, fig.cap = "Physical activity by sleep efficiency moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Ses.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-ses, fig.cap = "Physical activity by sleep onset moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Ses.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-ses, fig.cap = "Physical activity by sleep regularity moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Ses.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-sex, fig.cap = "Physical activity by sleep duration moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Sex.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-sex, fig.cap = "Physical activity by sleep efficiency moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Sex.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-sex, fig.cap = "Physical activity by sleep onset moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Sex.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-sex, fig.cap = "Physical activity by sleep regularity moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Sex.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-weekday, fig.cap = "Physical activity by sleep duration moderated by weekday"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Weekday_x.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-weekday, fig.cap = "Physical activity by sleep efficiency moderated by weekday"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Weekday_x.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-weekday, fig.cap = "Physical activity by sleep onset moderated by weekday"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Weekday_x.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-weekday, fig.cap = "Physical activity by sleep regularity moderated by weekday"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Weekday_x.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-season, fig.cap = "Physical activity by sleep duration moderated by season"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Season.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-season, fig.cap = "Physical activity by sleep efficiency moderated by season"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Season.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-season, fig.cap = "Physical activity by sleep onset moderated by season"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Season.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-season, fig.cap = "Physical activity by sleep regularity moderated by season"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Season.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-region, fig.cap = "Physical activity by sleep duration moderated by region"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Region.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-region, fig.cap = "Physical activity by sleep efficiency moderated by region"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Region.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-region, fig.cap = "Physical activity by sleep onset moderated by region"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Region.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-region, fig.cap = "Physical activity by sleep regularity moderated by region"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Region.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-daylight, fig.cap = "Physical activity by sleep duration moderated by daylight hours"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Daylight_hours.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-daylight, fig.cap = "Physical activity by sleep efficiency moderated by daylight hours"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Daylight_hours.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-daylight, fig.cap = "Physical activity by sleep onset moderated by daylight hours"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Daylight_hours.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-daylight, fig.cap = "Physical activity by sleep regularity moderated by daylight hours"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Daylight_hours.jpg"), error = FALSE)
```
\clearpage

@@

```{r PA-by-sleep-duration-fig-by-wear-location, fig.cap = "Physical activity by sleep duration moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-wear-location, fig.cap = "Physical activity by sleep efficiency moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-wear-location, fig.cap = "Physical activity by sleep onset moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

<!-- Finish auto-generated chunks go here: -->
